Word Learning as Network Growth: A Cross-linguistic Analysis

### 2018-11-12 journal/ms.tex
journal corrections

  \abstract{Children tend to produce words earlier when they are connected to a
variety of other words along both the phonological and semantic
dimensions. Though this connectivity effect has been extensively
documented, little is known about the underlying developmental
mechanism. One view suggests that learning is primarily driven by a
network growth model where highly connected words in the child's early
lexicon attract similar words. Another view suggests that learning is
driven by highly connected words in the external learning environment
instead of highly connected words in the early internal lexicon. The
present study tests both scenarios systematically in both the
phonological and semantic domains across 10 languages. We show that
external connectivity in the learning environment drives growth in both
production- and comprehension-based vocabularies. The findings suggest a
word learning mechanism where children harness their statistical
learning abilities to (indirectly) detect and learn highly connected
words in the learning environment.}
  \keywords{Language understanding; audio-visual processing; word learning; speech
perception; computational modeling. \\

@@

Besides these word-level properties, the lexical structure (that is, how
words relate to each other) also influences the age of acquisition of
words. The lexical structure can be characterized in terms of a network
where each node represents a word in the vocabulary, and each link
between two nodes represents a relationship between the corresponding
pair of words (e.g., Collins and Loftus, 1975). Previous studies have
investigated early vocabulary structure by constructing networks using a
variety of word-word relations including shared semantic features,
target-cue relationships in free association norms, co-occurrence in
child directed speech, and phonological relatedness. These studies have
found that children tend to produce words that have higher neighborhood
density (i.e., high connectivity in the network) earlier, both at the
phonological and the semantic level (Carlson, Sonderegger, \& Bane,
2014; Hills, Maouene, Riordan, \& Smith, 2010; Hills, Maouene, Maouene,
Sheya, \& Smith, 2009; Stella, Beckage, \& Brede, 2017; Storkel, 2009).

While most studies have focused on the static properties of the lexical
network, a few have investigated the underlying developmental process.
In particular, Steyvers and Tenenbaum (2005) suggested that the observed
effects of connectivity are the consequence of how the lexical network
gets constructed in the child's mind. According to this explanation,
known as Preferential Attachment, highly connected words in the child's
lexicon tend to \enquote{attract} more words over time, in a
rich-get-richer scenario (Barabasi \& Albert, 1999). In other words,
what predicts word learning is the \emph{internal} connectivity in the
child's early lexicon. In contrast, Hills et al. (2009) suggested that
what biases the learning is not the connectivity in the child's internal
lexicon but, rather, \emph{external} connectivity in the learning
environment. They called this alternative explanation Preferential
Acquisition. For clarity of reading, we will call preferential
attachment the Internally-driven mechanism (INT), and preferential
acquisition the Externally-driven mechanism (EXT).
Figure~\ref{fig:growth} shows an illustration of both growth scenarios
with the same simplified network. These two proposals represent two
divergent ideas about the role of lexical networks in acquisition. On
the INT proposal, network structure is a causal factor in early word
learning; in contrast, on the EXT approach, network structure is not
internally represented and, therefore, might be an epiphenomenon of the
statistics of the linguistic input.

@@

Hills et al. (2009) found that early lexical networks do not grow
through INT as was originally hypothesised by Steyvers and Tenenbaum
(2005), but rather through EXT. This finding, though potentially very
profound, has only been established in the special case of networks that
are based on 1) semantic associations, 2) production-based vocabularies,
and 2) data from English-learning children, only. The extent to which
this result depends on the domain, the measure and culture/language is
still unclear. In this work, we test the generality of the finding along
these three dimensions.

First, we study the phonological network in addition to the semantic
network. These two networks represent different ways the mental lexicon
is structured. In particular, words that are neighbors in the semantic
network (e.g., \enquote{cat}, \enquote{dog}) are not necessarily
neighbors in the phonological network, and vice versa. Does the
phonological network also influence word learning? Previous work did
find an effect of words' connectivity in the phonological network on
their age of learning (Carlson et al., 2014; Stella et al., 2017;
Storkel, 2009). In other words, words learned earlier in life tend to
sound similar to many other words than a word learned later in life.
However, this finding is compatible with both INT and EXT, and previous
studies did not explicitly compare these two mechanisms. Here, we
investigate whether phonological networks, like semantic networks, grow
through EXT, or if they rather grow via INT (Figure~\ref{fig:growth}).

@@

Finally, we use developmental data in 10 languages. Lexical networks can
show more or less cross-linguistic variability along both the semantic
and phonological domains (Arbesman, Strogatz, \& Vitevitch, 2010; Youn
et al.,
2016).\footnote{The difference is more obvious in the phonological case where the network structure––and the distribution of word connectivity––can a priori change from language to language depending on various languistic conventions.}
Besides, cultures might differ in the way caregivers talk to children
(Cristia, Dupoux, Gurven, \& Stieglitz, 2017; Kuhl et al., 1997), and
this difference in the input could influence the chidlren's learning
strategy. Thus, Cross-linguistic comparison is crucial to test what
mechanism is cognitively universal and is used by all children, and what
mechanism is specific to some patterns of learning that emerge due to
the particulars of a given language or culture (Bates \& MacWhinney,
1987; Slobin, 2014).

@@

We used data from Wordbank (Frank, Braginsky, Yurovsky, \& Marchman,
2017), an open repository aggregating cross-linguistic language
developmental data of the MacArthur-Bates Communicative Development
Inventory (CDI), a parent report vocabulary checklist. Parent report is
a reliable and valid measure of children's vocabulary that allows for
the cost-effective collection of datasets large enough to test
network-based models of acquisition (Fenson et al., 1994). When filling
out a CDI form, caregivers are either invited to indicate whether their
child \enquote{understands} (comprehension) or \enquote{understands and
says} (production) each of about 400-700 words. For younger children
(e.g., 8 to 18 months in the English data), both comprehension and
production are queried, whereas for older children (16 to 36 months)
only production is queried. We use data from younger children to test
comprehension and data from older children to test production across 10
languages. Following previous studies (Hills et al., 2009; Storkel,
2009), we restrict our analysis to nouns. Table \ref{tab:stats} gives an
overview of the data.

@@

\caption{\label{tab:stats}Statistics for data from Wordbank.}
\centering
\begin{tabular}[t]{>{\bfseries}lrlrl}
\toprule
\multicolumn{1}{c}{} & \multicolumn{2}{c}{Comprehension} & \multicolumn{2}{c}{Production} \\
\cmidrule(l{2pt}r{2pt}){2-3} \cmidrule(l{2pt}r{2pt}){4-5}
Language & Nouns & Ages & Nouns & Ages\\
\midrule
Croatian & 209 & 8-16 & 312 & 16-30\\
Danish & 200 & 8-20 & 316 & 16-36\\
English & 209 & 8-18 & 312 & 16-30\\
French & 197 & 8-16 & 307 & 16-30\\
Italian & 209 & 7-24 & 312 & 18-36\\
Norwegian & 193 & 8-20 & 316 & 16-36\\
Russian & 207 & 8-18 & 314 & 18-36\\
Spanish & 208 & 8-18 & 312 & 16-30\\
Swedish & 205 & 8-16 & 339 & 16-28\\
Turkish & 180 & 8-16 & 297 & 16-36\\
\bottomrule
\end{tabular}
\end{table}

@@

Since the free association norms are available only in English, we used
the hand-checked translation equivalents available in Wordbank, which
allowed us to use the English association norms across languages. Using
the same association data across languages does not necessarily mean
that the resulting networks will be the same across languages, or that
these networks will grow similarly. Indeed, though this approximation
assumes that the semantic similarity measure is universal----which is a
reasonable assumption (e.g., Youn et al. 2015), the set of words
acquired by children as well as the timeline of this acquisition can
still vary from language to language leading to possibility different
learning strategies.

@@

The plots show, overall, a negative correlation between the month of
acquisition and the degree. In production data, the average correlation
across languages was -0.24 (SD=0.10) for the semantic networks and -0.30
(SD=0.05) for the phonological networks. In comprehension data, the
average correlation was -0.21 (SD=0.08) for the semantic networks and
-0.21 (SD=0.07) for the phonological networks. These results indicate
that nouns with higher degrees are generally learned earlier, thus
replicating previous findings in English (e.g., Storkel 2004, 2009;
Hills et al. 2009) and extending these findings to ten different
languages (with few exceptions) in both production- and
comprehension-based vocabularies.

@@

We also analyzed the global network's degree distribution. The shape of
this distribution is particularly relevant to INT as this growth
scenario is known to generate networks with a power-law degree
distribution, i.e., a distribution of the form
\(p(k) \propto \frac{1}{k^{\alpha}}\) (Barabasi \& Albert, 1999). If the
network displays this property, this fact would suggest an INT-like
generative process. Conversely, if the degree distribution does not
follow a power law, this fact would weaken the case for INT. The log-log
plots are shown in Figure \ref{fig:degreeDist}. We fit a power law to
each empirical degree distribution following the procedure outlined in
Clauset, Shalizi, and Newman (2009) and using a related R package
(poweRlaw, Gillespie, 2015).

@@

Overall, we could not reject the null hypothesis of a power-law
distribution: The \(p\)-value was generally above 0.1 in almost all
languages for both production and comprehension. That said, phonological
networks had relatively larger cut-offs than semantic networks. As was
suggested by Arbesman et al. (2010), these \enquote{truncated}
power-laws in phonological networks ----as well as the observed
cross-linguistic variability in the value of the cut-offs---- may
reflect the various constraints that exist on word formation such as the
number of phonemes in the language, the phonotactics (i.e., the way
sound sequences are arranged in words), and the length of words. Such
constraints may limit the number of words that are phonologically
similar, thus leading to distributions which decay faster than a
non-truncated power law.

@@

Above we showed that the way semantic and phonological information is
structured in the learning environment contributes to noun learning (via
EXT) across languages. However, we know that other factors influence
learning as well (e.g., Braginsky et al., 2016). Next we investigated
how semantic and phonological connectivity interact with two other
factors. The first one is word frequency, a well studied factor shown to
predict the age of acquisition in a reliable fashion (e.g. J. C. Goodman
et al., 2008). The second factor is word length, which was shown to
correlate with phonological connectivity: Shorter words are more likely
to have higher connectivity (Pisoni et al., 1985; Vitevitch and
Rodriguez, 2004).

@@

For word length, we counted the number of phonemes in our generated IPA
transcription. For word frequency, we used the frequency estimates from
Braginsky et al. (2016) where unigram counts were derived based on
CHILDES corpora in each language (MacWhinney, 2000). For each word,
counts included words that shared the same stem (e.g., \enquote{cats}
counts as \enquote{cat}), or words that were synonymous (e.g.
\enquote{father} counts as \enquote{daddy}). Although these frequency
counts use transcripts from independent sets of children, they are based
on large samples, and this allows us to average out possible differences
between children and the specificities of their input (see Goodman et
al. 2008).

@@

As for the factors of interest, i.e., semantic and phonological
connectivity, we found cross-linguistic differences. Connectivity
contributes to learning in some languages but not in other. In
particular, semantic connectivity does not explain variance in English
data beyond that explained by phonological connectivity, frequency and
length. This contrasts with the original finding in Hills et al. (2009).
However, in this previous study, semantic connectivity was not tested in
a model that included frequency, length and phonological connectivity as
covariates. Another important difference is the number of words tested:
Our study uses a larger set of nouns. That said, and despite these
apparent cross-linguistic differences, both phonological and semantic
connectivity are significant predictors in the combined model.

@@

This study provided an analysis of network growth during development. We
compared two network growth scenarios described in the pioneering work
of Steyvers and Tenenbaum (2005) and Hills et al. (2009). The first
scenario, INT (originally called Preferential Attachment), described a
rich-get-richer network growth model in which the current structure of
the learner's internal network determines future growth; the other, EXT
(originally called Preferential Acquisition) described a model in which
the external, global environmental network structure determines
learners' growth patterns. These two mechanisms represent two
fundamentally different accounts of lexical growth: one suggests that
future word knowledge is primarily shaped by the children's past
knowledge and its organization, whereas the other suggests that learning
is shaped, rather, by salient properties in the input regardless of how
past knowledge is organized.

Previous work (Hills et al., 2010, 2009) has been limited in its scope:
It focused primarily on semantic networks, production-based
vocabularies, and developmental data from English-learning children. The
present study tested the generality of previous findings by 1)
investigating phonological networks together with semantic networks, 2)
testing both comprehension- and production-based vocabularies, and 3)
comparing the results across 10 languages.

@@

These findings corroborate the hypothesis that children start by
learning words that have high similarity to a variety of other words in
the learning environment, not in the child's available lexicon. This
means, strikingly, that children are sensitive to highly connected words
although they do not initially have access to the full network. This
finding raises some important questions. What mechanism allows children
to distinguish highly connected words from other words? Besides, why
would highly connected words be easier to learn?

One possibility is that children rely on their statistical learning
abilities. For example, in the semantic domain, children might be using
a mechanism akin to cross-situational learning to pick up the meanings
of some words, especially concrete nouns (Smith \& Yu, 2008), and such
learning would resemble the growth scenario described by EXT. Indeed,
since free association is related to contextual co-occurrence (Griffiths
et al., 2007), highly connected words will tend to occur in a variety of
speech and referential contexts. This fact makes such words easier to
learnonly because they have more referential disambiguating cues across
learning contexts, and crucially, even without knowing the entire set of
words with witch they occurs (hence the similarity with EXT). This
possibility is supported by the finding that words' diversity of
occurrence in child directed speech predicts their age of learning
(Hills et al., 2010).

In the phonological case, network growth according to EXT is also
compatible with a scenario whereby children are tracking lwo level
statistical patterns, e.g., high probability sound sequences. Indeed,
connectivity in the phonological network is inherently correlated with
phonotactic probability (M. S. Vitevitch, Luce, Pisoni, \& Auer, 1999).
That is, highly connected words tend to be made of frequent sound
sequences. Children are sensitive to local phonotactic regularities
(Jusczyk, Luce, \& Charles-Luce, 1994) and this sensitivity might lead
them to learn higher-probability words more easily (e.g., Storkel,
2001). This explanation is supported by computational simulations that
shows how learning general phonotactics patterns create ``well-worn
paths'' which allow the models to represent several distinct but
phonologically neighboring words (Dell et al; 1993; Takac et al. 2017).

Besides using their own statistical learning skills, children could also
benefit from the way their caregivers speak. Perhaps the caregivers put
more emphasis on the words that are highly connected in \emph{their}
mature lexical network. This emphasis would guide children to learn
first these highly connected words even though children do not have
access to the distribution of words' connectivity in the final network.
Investigating this possibility would require further research on
caregiver-child interaction (MacWhinney, 2014; B. C. Roy et al., 2015),
examining what words are introduced over development and the extent to
which children's uptake is influenced by this input (Clark 2007; Hoff
and Naigles, 2002; Hurtado et al., 2008).

This work shares a number of limitations with previous studies using
similar research strategy and datasets (e.g., Hills et al. 2009; 2010).
Chief among these limitations is the fact that the age of word
acquisition is computed using different children at different ages (due
to the fact that available CDI data is mainly cross-sectional). Although
this measure has proven highly consistent (Fensen et al. 1994), it lead
us to focus on studying the learning mechanism of the \enquote{average}
child. Individual trajectories, however, could show different learning
patterns. For example, using longitudinal data Beckage, Smith, and Hills
(2011) found differences between typical and late talkers in terms of
the semantic network structure. Besides, although our study endorses the
externally-driven account of network growth, this does not mean
individual children never use some variant of INT or some combination of
both INT and EXT (Beckage and Colunga, under review). For example, some
children develop \enquote{islands of expertise}, that is, well organized
knowledge about a certain topic (e.g., birds or dinosaurs). This prior
knowledge enables these children to learn new related words more easily
(e.g., Chi and Koeske, 1983).

@@

@@

@@

@@

@@

@@

@@

@@

@@

\hypertarget{ref-smith2008}{}
Smith, L., \& Yu, C. (2008). Infants rapidly learn word-referent
mappings via cross-situational statistics. \emph{Cognition},
\emph{106}(3), 1558--1568.

@@

>>>>

  \abstract{Children tend to produce words earlier when they are connected to a
variety of other words along both the phonological and semantic
dimensions. Though this connectivity effect has been extensively
documented, little is known about the underlying developmental
mechanism. One view suggests that learning is primarily driven by a
network growth model where highly connected words in the child's early
lexicon attract similar words. Another view suggests that learning is
driven by highly connected words in the external learning environment,
instead of highly connected words in the early internal lexicon. The
present study tests both scenarios systematically in both the
phonological and semantic domains across 10 languages. We show that
external connectivity in the learning environment drives growth in both
production- and comprehension-based vocabularies, even controlling for
word frequency and length. This pattern of findings suggests a word
learning mechanism where children harness their statistical learning
abilities to (indirectly) detect and learn highly connected words in the
learning environment.}
  \keywords{Language understanding; audio-visual processing; word learning; speech
perception; computational modeling. \\

@@

Besides these word-level properties, the structure of the lexicon (that
is, how words relate to each other) also predicts the age of acquisition
of words. The lexical structure can be characterized in terms of a
network where each node represents a word in the vocabulary, and each
link between two nodes represents a relationship between the
corresponding pair of words (e.g., Collins \& Loftus, 1975). Previous
studies have investigated early vocabulary structure by constructing
networks using a variety of word-word relations including shared
semantic features, target-cue relationships in free association norms,
co-occurrence in child directed speech, and phonological relatedness.
These studies have found that children tend to produce words that have
higher neighborhood density (i.e., high connectivity in the network)
earlier, both at the phonological and the semantic level (Carlson,
Sonderegger, \& Bane, 2014; Hills, Maouene, Riordan, \& Smith, 2010;
Hills, Maouene, Maouene, Sheya, \& Smith, 2009; Stella, Beckage, \&
Brede, 2017; Storkel, 2009).

While most studies have focused on the static properties of the lexical
network, a few have investigated the underlying developmental process.
In particular, Steyvers and Tenenbaum (2005) suggested that the observed
effects of connectivity are the consequence of how the lexical network
gets constructed in the child's mind. According to this explanation,
known as Preferential Attachment, highly connected words in the child's
lexicon tend to \enquote{attract} more words over time, in a
rich-get-richer scenario (Barabasi \& Albert, 1999). In other words,
what predicts word learning is the \emph{internal} connectivity in the
child's early lexicon. In contrast, Hills et al. (2009) suggested that
what biases the learning is not the connectivity in the child's internal
lexicon but, rather, \emph{external} connectivity in the learning
environment. They called this alternative explanation Preferential
Acquisition. For clarity of reading, we will call preferential
attachment the Internally-driven mechanism (INT), and preferential
acquisition the Externally-driven mechanism (EXT).
Figure~\ref{fig:growth} shows an illustration of both growth scenarios
with the same simplified network.

These two proposals represent two divergent ideas about the role of
lexical networks in acquisition. On the INT proposal, learning is driven
by known words with high connectivity to other known words (Figure 1,
left). Thus, the network structure is a causal factor in early word
learning, that is, children might be relying on the organization of
their past knowledge to determine future learning. For example, having a
rich and organized knowledge about the domain of dinosaurs would
facilitate the acquisition of new dinosaur-related words (Chi \& Koeske,
1983). In contrast, on the EXT approach, learning is driven by the
connectivity of words that are not known yet (Figure 1, right). Thus,
the relevant network structure is not internally represented by
children, and the related connectivity effect might be an epiphenomenon
of some low level properties of the linguistic input. For example,
highly connected words in the input could be more easily learned because
of their contextual diversity (e.g., Smith \& Yu, 2008) or because
caregivers emphasize such words in child-directed speech (MacWhinney,
2014).

@@

Hills et al. (2009) investigated the growth of lexico-semantic networks
in toddlers and found that growth did not proceed according to INT as
was originally hypothesised by Steyvers and Tenenbaum (2005), but rather
according to
EXT.\footnote{Besides INT and EXT, the authors tested a third mechanism (called the lure of associates) which resembles EXT in that it is driven by the connectivity of external nodes, except that this connectivity is computed with respect to words that are known. However, EXT is the externally-driven scenario that best predicted the data in this previous work.}
This is a profound finding because it suggests that learning in the
early stages is mostly driven by properties of the external input,
regardless of how past knowledge is organized. However, this work has
been done in the special case of networks that are based on 1) semantic
associations, 2) production-based vocabularies, and 2) data from
English-learning children, only. The extent to which this result depends
on the domain (e.g., semantic vs.~phonological connectivity), the
vocabulary measure (production vs.~comprehension) and culture/language
is still unclear. In this work, we test the generality of the finding
along these three dimensions.

First, we study the phonological network in addition to the semantic
network. These two networks represent different ways the mental lexicon
is structured. In particular, words that are neighbors in the semantic
network (e.g., \enquote{cat}, \enquote{dog}) are not necessarily
neighbors in the phonological network, and vice versa. Does the
phonological network also predict word learning? Previous work did find
an effect of words' connectivity in the phonological network on their
age of learning (Carlson et al., 2014; Stella et al., 2017; Storkel,
2009). In other words, words learned earlier in life tend to sound
similar to many other words than a word learned later in life. However,
this finding is \emph{a priori} compatible with both INT and EXT, and
previous studies did not explicitly compare these two mechanisms. Here,
we investigate whether phonological networks, like semantic networks,
grow through EXT, or if they rather grow via INT
(Figure~\ref{fig:growth}).

@@

Finally, we use developmental data in 10 languages. Lexical networks can
show more or less cross-linguistic variability along both the semantic
and phonological domains (Arbesman, Strogatz, \& Vitevitch, 2010; Youn
et al., 2016). Besides, cultures might differ in the way caregivers talk
to children (Cristia, Dupoux, Gurven, \& Stieglitz, 2017; Kuhl et al.,
1997), and this difference in the input could influence the children's
learning strategy. Thus, Cross-linguistic comparison is crucial to test
what mechanism is cognitively universal and is used by all children, and
what mechanism is specific to some patterns of learning that emerge due
to the particulars of a given language or culture (Bates \& MacWhinney,
1987; Slobin, 2014).

We test the growth scenarios using parent reports of children
vocabularies and their normative age of acquisition (Fenson et al.,
1994). Children may vary in their individual learning trajectories, but
the aggregate data leads to an average learning pattern which is highly
consistent. It is this normative trajectory that we model in the current
study, following the steps of previous research using similar datasets
(Braginsky et al., 2016; J. C. Goodman et al., 2008; Hills et al., 2010,
2009; Stella et al., 2017; Storkel, 2009)

@@

We used data from Wordbank (Frank, Braginsky, Yurovsky, \& Marchman,
2017), an open repository aggregating cross-linguistic language
developmental data of the MacArthur-Bates Communicative Development
Inventory (CDI), a parent report vocabulary checklist. Parent report is
a reliable and valid measure of children's vocabulary that allows for
the cost-effective collection of datasets large enough to test
network-based models of acquisition (Fenson et al., 1994). When filling
out a CDI form, caregivers are either invited to indicate whether their
child \enquote{understands} (comprehension) or \enquote{understands and
says} (production) each of about 400-700 words. For younger children
(e.g., 8 to 18 months in the English data), both comprehension and
production are queried, whereas for older children (16 to 36 months)
only production is queried. Thus, we use data from younger children to
test comprehension and data from older children to test production
across 10 languages. Following previous studies (Hills et al., 2009;
Storkel, 2009), we restrict our analysis to nouns. Table \ref{tab:stats}
gives an overview of the data.

@@

\caption{\label{tab:stats}Statistics for dataset we used.}
\centering
\begin{tabular}[t]{>{\bfseries}lrlrl}
\toprule
\multicolumn{1}{c}{} & \multicolumn{2}{c}{Comprehension} & \multicolumn{2}{c}{Production} \\
\cmidrule(l{2pt}r{2pt}){2-3} \cmidrule(l{2pt}r{2pt}){4-5}
Language & Nouns & Ages & Nouns & Ages\\
\midrule
Croatian & 209 & 8-16 & 312 & 16-30\\
Danish & 200 & 8-20 & 316 & 16-36\\
English & 209 & 8-18 & 312 & 16-30\\
French & 197 & 8-16 & 307 & 16-30\\
Italian & 209 & 7-24 & 312 & 18-36\\
Norwegian & 193 & 8-20 & 316 & 16-36\\
Russian & 207 & 8-18 & 314 & 18-36\\
Spanish & 208 & 8-18 & 312 & 16-30\\
Swedish & 205 & 8-16 & 339 & 16-28\\
Turkish & 180 & 8-16 & 297 & 16-36\\
\bottomrule
\end{tabular}
\end{table}

@@

Since the free association norms are available only in English, we used
the hand-checked translation equivalents available in Wordbank, which
allowed us to use the English association norms across languages. Using
the same association data across languages does not necessarily mean
that the resulting networks will be the same across languages, or that
these networks will grow similarly. Indeed, though this approximation
assumes that the semantic similarity measure is universal----which is a
reasonable assumption (e.g., Youn et al., 2016), the set of words
acquired by children as well as the timeline of this acquisition can
still vary from language to language leading to possibility different
learning strategies.

@@

The plots show, overall, a negative correlation between the month of
acquisition and the degree. In production data, the average correlation
across languages was -0.24 (SD=0.10) for the semantic networks and -0.30
(SD=0.05) for the phonological networks. In comprehension data, the
average correlation was -0.21 (SD=0.08) for the semantic networks and
-0.21 (SD=0.07) for the phonological networks. These results indicate
that nouns with higher degrees are generally learned earlier, thus
replicating previous findings in English (e.g., Storkel 2004, 2009;
Hills et al. 2009) and extending these findings to ten different
languages, generally, in both production- and comprehension-based
vocabularies.

@@

We also analyzed the global network's degree distribution. The shape of
this distribution is particularly relevant to INT as this growth
scenario is known to generate networks with a power-law degree
distribution, i.e., a distribution of the form
\(p(k) \propto \frac{1}{k^{\alpha}}\) (Barabasi \& Albert, 1999). If the
network displays this property, this fact would suggest, but not prove,
an INT-like generative process. If the degree distribution does not
follow a power law, this would largely weaken the case for INT. The
log-log plots are shown in Figure \ref{fig:degreeDist}. We fit a power
law to each empirical degree distribution following the procedure
outlined in Clauset, Shalizi, and Newman (2009) and using a related R
package (poweRlaw, Gillespie, 2015).

@@

Overall, we could not reject the null hypothesis of a power-law
distribution: The \(p\)-value was generally above 0.1 in almost all
languages for both production and comprehension. That said, phonological
networks had relatively larger cut-offs than semantic networks. As was
suggested by Arbesman et al. (2010), these \enquote{truncated}
power-laws in phonological networks--as well as the observed
cross-linguistic variability in the value of the cut-offs--may reflect
the various constraints that exist on word formation such as the number
of phonemes in the language, the phonotactics (i.e., the way sound
sequences are arranged in words), and the length of words. Such
constraints may limit the number of words that are phonologically
similar, thus leading to distributions which decay faster than a
non-truncated power law.

@@

Above we showed that the way semantic and phonological information is
structured in the learning environment contributes to noun learning (via
EXT) across languages. However, we know that other factors influence
learning as well (e.g., Braginsky et al., 2016). Next we investigated
how semantic and phonological connectivity interact with two other
factors. The first one is word frequency, a well studied factor shown to
predict the age of acquisition in a reliable fashion (e.g. J. C. Goodman
et al., 2008). The second factor is word length, which was shown to
correlate with phonological connectivity: Shorter words are more likely
to have higher connectivity (Pisoni, Nusbaum, Luce, \& Slowiaczek, 1985;
Vitevitch \& Rodríguez, 2005).

@@

For word length, we counted the number of phonemes in our generated IPA
transcription. For word frequency, we used the frequency estimates from
Braginsky et al. (2016) where unigram counts were derived based on
CHILDES corpora in each language (MacWhinney, 2014). For each word,
counts included words that shared the same stem (e.g., \enquote{cats}
counts as \enquote{cat}), or words that were synonymous (e.g.
\enquote{father} counts as \enquote{daddy}). Although these frequency
counts use transcripts from independent sets of children, they are based
on large samples, and this allows us to average out possible differences
between children and the specificities of their input (see J. C. Goodman
et al., 2008).

@@

As for the factors of interest, i.e., semantic and phonological
connectivity, we found cross-linguistic differences. Connectivity
contributes to learning in some languages but not in other. In
particular, semantic connectivity does not explain variance in English
data beyond that explained by phonological connectivity, frequency and
length. This contrasts with the original finding in Hills et al. (2009).
However, this might be due to our using of a slightly different model
(which included word length as a covariate) and a larger dataset. That
said, and despite these apparent cross-linguistic differences, both
phonological and semantic connectivity are significant predictors in the
combined model.

@@

This study provided an analysis of network growth during development. We
compared two network growth scenarios described in the pioneering work
of Steyvers and Tenenbaum (2005) and Hills et al. (2009). The first
scenario, INT (originally called Preferential Attachment), described a
rich-get-richer network growth model in which the current structure of
the learner's internal network determines future growth; the other, EXT
(originally called Preferential Acquisition) described a model in which
the external, global environmental network structure determines
learners' growth patterns. These two mechanisms represent two
fundamentally different accounts of lexical growth: One suggests that
future word knowledge is primarily shaped by the children's past
knowledge and its organization, whereas the other suggests that learning
is shaped, rather, by salient properties in the input regardless of how
past knowledge is organized. The present study tested the generality of
previous findings (Hills et al., 2010, 2009) by 1) investigating
phonological networks together with semantic networks, 2) testing both
comprehension- and production-based vocabularies, and 3) comparing the
results across 10 languages.

@@

These findings corroborate the hypothesis that children start by
learning words that have high similarity to a variety of other words in
the learning environment, not in the child's available lexicon. This
hypothesis implies that children are sensitive to highly connected words
although they do not initially have access to the full network, thus
raising some important questions: What mechanism allows children to
distinguish highly connected words from other words? Besides, why would
highly connected words be easier to learn?

One possibility is that these patterns emerge from children's use of
statistical learning abilities (Aslin \& Newport, 2012; Saffran, Aslin,
\& Newport, 1996; Smith \& Yu, 2008). The term \enquote{statistical
learning} has been used in the developmental literature to describes the
process by which one acquires information about their environment
through keeping track of the frequency distribution of some elements
(e.g., words) in different contexts. An important property of this kind
of learning is that it occurs without explicit instructions and through
mere exposure to the input. Previous work in the line of research has
documented mechanisms which can explain the patterns found in the
current study.

For example, in the semantic domain, growth according to EXT can be
explained by a mechanism similar to cross-situational learning (Pinker,
2013; Smith \& Yu, 2008; Yurovsky \& Frank, 2015). According to this
mechanism, children track the co-occurrence of concrete nouns with their
possible semantic referents. The referent of a word heard in only one
naming situation can be ambiguous (e.g., when the word \enquote{ball} is
heard for the first time in the presence of both a ball and a chair),
but hearing the same word in a diversity of semantic contexts allows the
learner to narrow down the set of possible word-object mappings. In our
case, free association is related to contextual co-occurrence
(Griffiths, Steyvers, \& Tenenbaum, 2007), meaning that highly connected
words will tend to occur in a variety of speech and referential
contexts. This fact makes such words easier to learn because they have
more referential disambiguating cues across learning contexts, and
crucially, even without knowing the entire set of words with witch they
co-occur (hence the similarity with EXT). This possibility is supported
by the finding that words' diversity of occurrence in child directed
speech predicts their age of learning (Hills et al., 2010).

In the phonological case, network growth according to EXT is also
compatible with a scenario whereby children are tracking lwo level
statistical patterns, e.g., high probability sound sequences. Indeed,
connectivity in the phonological network is inherently correlated with
phonotactic probability (M. S. Vitevitch, Luce, Pisoni, \& Auer, 1999).
That is, highly connected words tend to be made of frequent sound
sequences. Children are sensitive to local phonotactic regularities
(Jusczyk, Luce, \& Charles-Luce, 1994) and this sensitivity might lead
them to learn higher-probability words more easily (Storkel, 2001). This
explanation is supported by computational simulations that shows how
learning general phonotactics patterns create ``well-worn paths'' which
allow the models to represent several distinct but phonologically
neighboring words (Dell, Juliano, \& Govindjee, 1993; Takac, Knott, \&
Stokes, 2017).

Besides using their own statistical learning skills, children could also
benefit from the way their caregivers speak. Perhaps the caregivers put
more emphasis on the words that are highly connected in \emph{their}
mature lexical network. This emphasis would guide children to learn
first these highly connected words even though children do not have
access to the distribution of words' connectivity in the final network.
Investigating this possibility would require further research on
caregiver-child interaction (MacWhinney, 2014; B. C. Roy et al., 2015),
examining what words are introduced over development and the extent to
which children's uptake is influenced by this input (Clark, 2007; Hoff
\& Naigles, 2002).

This work shares a number of limitations with previous studies using
similar research strategy and datasets. Chief among these limitations is
the fact that the age of word acquisition is computed using different
children at different ages (due to the fact that available CDI data is
mainly cross-sectional). Although this measure has proven highly
consistent (Fenson et al., 1994), it led us to focus on studying the
learning mechanism of the \enquote{average} child. Individual
trajectories, however, could show different learning patterns. For
example, using longitudinal data Beckage, Smith, and Hills (2011) found
differences between typical and late talkers in terms of the semantic
network structure. Besides, although our study endorses the
externally-driven account of network growth, this does not mean
individual children never use some variant of INT or some combination of
both INT and EXT (Beckage and Colunga, under review). For example, some
children develop \enquote{islands of expertise}, that is, well organized
knowledge about a certain topic (e.g., birds or dinosaurs). This prior
knowledge enables these children to learn new related words more easily
(e.g., Chi \& Koeske, 1983).

@@

\hypertarget{ref-aslin2012}{}
Aslin, R. N., \& Newport, E. L. (2012). Statistical learning: From
acquiring specific items to forming general rules. \emph{Current
Directions in Psychological Science}, \emph{21}(3).

@@

\hypertarget{ref-chi1983}{}
Chi, M. T., \& Koeske, R. D. (1983). Network representation of a child's
dinosaur knowledge. \emph{Developmental Psychology}, \emph{19}(1).

\hypertarget{ref-clark2007}{}
Clark, E. V. (2007). Young children's uptake of new words in
conversation. \emph{Language in Society}, \emph{36}(2).

@@

\hypertarget{ref-collins1975}{}
Collins, A. M., \& Loftus, E. F. (1975). A spreading-activation theory
of semantic processing. \emph{Psychological Review}, \emph{82}(6).

@@

\hypertarget{ref-dell1993}{}
Dell, G. S., Juliano, C., \& Govindjee, A. (1993). Structure and content
in language production: A theory of frame constraints in phonological
speech errors. \emph{Cognitive Science}, \emph{17}(2), 149--195.

@@

\hypertarget{ref-griffiths07}{}
Griffiths, T. L., Steyvers, M., \& Tenenbaum, J. B. (2007). Topics in
semantic representation. \emph{Psychological Review}, \emph{114}(2),
2007.

@@

\hypertarget{ref-hoff2002}{}
Hoff, E., \& Naigles, L. (2002). How children use input to acquire a
lexicon. \emph{Child Development}, \emph{73}(2).

@@

\hypertarget{ref-pinker2013}{}
Pinker, S. (2013). \emph{Learnability and cognition: The acquisition of
argument structure}. MIT press.

\hypertarget{ref-pisoni1985}{}
Pisoni, D. B., Nusbaum, H. C., Luce, P. A., \& Slowiaczek, L. M. (1985).
Speech perception, word recognition and the structure of the lexicon.
\emph{Speech Communication}, \emph{4}(1), 75--95.

@@

\hypertarget{ref-saffran1996}{}
Saffran, J. R., Aslin, R. N., \& Newport, E. L. (1996). Statistical
learning by 8-month-old infants. \emph{Science}, \emph{274}(5294),
1926--1928.

@@

\hypertarget{ref-smith2008}{}
Smith, L., \& Yu, C. (2008). Infants rapidly learn word-referent
mappings via cross-situational statistics. \emph{Cognition},
\emph{106}(3).

@@

\hypertarget{ref-takac2017}{}
Takac, M., Knott, A., \& Stokes, S. (2017). What can neighbourhood
density effects tell us about word learning? Insights from a
connectionist model of vocabulary development. \emph{Journal of Child
Language}, \emph{44}(2).

\hypertarget{ref-vitevitch2005}{}
Vitevitch, M. S., \& Rodríguez, E. (2005). Neighborhood density effects
in spoken word recognition in spanish. \emph{Journal of Multilingual
Communication Disorders}, \emph{3}(1).
